Real-time Acoustic Ray Range Estimation for Underwater Vehicle Navigation

### 2021-08-26 doc/main.tex
fix pseudo* spelling

\begin{abstract}
Almost all underwater navigation paradigms rely on the conversion of recorded travel time into range to compute a trilateration solution.
For real-time navigation, this conversion is treated deterministically.
For positioning in post-processing, more computationally and/or labor intensive modeling methods are often employed to reduce the uncertainty driven by multipath arrivals.
An autonomous underwater vehicle deployment in March 2020 in the Beaufort Sea faced significant operational challenges with a total ice-covered environment and complex acoustic propagation via the Beaufort Lens.
We implement an embedded, stochastic, ray-based prediction of the horizontal group velocity and validate its performance with communication events between GPS-aided beacons, achieving a psuedorange mean absolute error of 11 m.
In post-processing, we introduce a multipath criterion and achieve ranging performance that rivals GPS.
To our knowledge, these results are the first field experiment to demonstrate a real-time, physics-based data processing to minimize ranging error in underwater navigation.
\end{abstract}

@@

Finally, the psuedorange is calculated simply as
\begin{equation}
r_{i,j} = u_{i,j} \Delta t_{i,j} 
\end{equation}

@@

\FloatBarrier
\section{\label{sec:realtime} Real-time psuedorange results}

The modem experiment generated 811 beacon to beacon communication events with their own real-time NBC group velocity predictions.
As expected, the algorithm is generally overestimating range as it resolves a direct path that does not represent the actual arrival.
This section examines the absolute range error between the psuedorange and the GPS derived range with the caveat that the data collected is fairly unbalanced across source depths and sound speed conditions.

@@

\FloatBarrier
\section{\label{sec:postprocess} Post-processing psuedorange results}

@@

\FloatBarrier
\subsection{Psuedorange error versus one way travel time}

@@

\FloatBarrier
\subsection{Psuedorange estimations from the nearest and minimal bounce criteria}

The previous section displayed the psuedorange performance using the NBC.
Here, we explicitly compare the ranging accuracy between the nearest and minimal bounce criteria for all events in the post-processing pipeline.
It is important to note that because the post-processing pipeline is the same for both methods, that the efficacy of the NBC compared to the MBC is 100\%, as the former simplifies to the latter for direct path classifications.

>>>>

\begin{abstract}
Almost all underwater navigation paradigms rely on the conversion of recorded travel time into range to compute a trilateration solution.
For real-time navigation, this conversion is treated deterministically.
For positioning in post-processing, more computationally and/or labor intensive modeling methods are often employed to reduce the uncertainty driven by multipath arrivals.
An autonomous underwater vehicle deployment in March 2020 in the Beaufort Sea faced significant operational challenges with a total ice-covered environment and complex acoustic propagation via the Beaufort Lens.
We implement an embedded, stochastic, ray-based prediction of the horizontal group velocity and validate its performance with communication events between GPS-aided beacons, achieving a pseudorange mean absolute error of 11 m.
In post-processing, we introduce a multipath criterion and achieve ranging performance that rivals GPS.
To our knowledge, these results are the first field experiment to demonstrate a real-time, physics-based data processing to minimize ranging error in underwater navigation.
\end{abstract}

@@

Finally, the pseudorange is calculated simply as
\begin{equation}
r_{i,j} = u_{i,j} \Delta t_{i,j} 
\end{equation}

@@

\FloatBarrier
\section{\label{sec:realtime} Real-time pseudorange results}

The modem experiment generated 811 beacon to beacon communication events with their own real-time NBC group velocity predictions.
As expected, the algorithm is generally overestimating range as it resolves a direct path that does not represent the actual arrival.
This section examines the absolute range error between the pseudorange and the GPS derived range with the caveat that the data collected is fairly unbalanced across source depths and sound speed conditions.

@@

\FloatBarrier
\section{\label{sec:postprocess} Post-processing pseudorange results}

@@

\FloatBarrier
\subsection{Pseudorange error versus one way travel time}

@@

\FloatBarrier
\subsection{Pseudorange estimations from the nearest and minimal bounce criteria}

The previous section displayed the pseudorange performance using the NBC.
Here, we explicitly compare the ranging accuracy between the nearest and minimal bounce criteria for all events in the post-processing pipeline.
It is important to note that because the post-processing pipeline is the same for both methods, that the efficacy of the NBC compared to the MBC is 100\%, as the former simplifies to the latter for direct path classifications.
